---
title: "Overview of `metalite.table1`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of `metalite.table1`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
library(r2rtf)
library(table1)
devtools::load_all()
```

# Motivation 

A table for descriptive statistics is widely used 
in medical research and typically be the first table (i.e. `table1`) 
for a manuscript. 

There are R packages and examples to create the table1: 

- [`table1`](https://github.com/benjaminrich/table1)

For use case in clinical trials, 
[Chapter 4 of the R for clinical study reports and submission](https://r4csr.org/baseline-characteristics.html) 
contains more details. 

The `metalite.table1` provide an interactive table1 to 
enhance the communication between statisticians and clinicians. 

```{r}
# Prepare analysis ready data 
df <- r2rtf_adsl
df$AGE[1:3] <- NA # Create missing value for illustration purpose. 
df$ARM <- factor(df$ARM, 
                 c("Placebo", "Xanomeline Low Dose", "Xanomeline High Dose"), 
                 c("Placebo", "Low Dose", "High Dose"))
```

```{r}
# Create interactive table1
metalite_table1(~ AGE + SEX + RACE + BMIBLGR1 | ARM, # formula for analysis variables and group 
                data = df,                           # source data
                id = "USUBJID")                      # unique subject id
```





